Temporal Split

### 2023-02-01 workflow/notebooks/temporal-split.Rmd

```{r perf_100_otu_vs_genus}
perf_dat_100 %>% 
  filter(method == 'glmnet', trainfrac == 0.8) %>% 
  ggplot(aes(x = .estimate, y = outcome, color = .term)) +
  geom_vline(xintercept = 0.5, linetype = 'dashed') +
  geom_boxplot() +
  xlim(0,1) +
  facet_wrap(c('dataset', 'taxlevel')) +
  coord_flip() +
  labs(title = '100x train/test splits - glmnet',
       caption = 'Box: interquartile range. Whisker: min & max') +
  theme_sovacool() +
  theme(legend.position = 'top',
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        plot.caption = element_text(hjust = 0)
  )
```

>>>>

```{r perf_100_otu_vs_genus, fig.width=10, fig.height=5}
perf_dat_100 %>% 
  filter(method == 'glmnet', trainfrac == 0.8) %>% 
  ggplot(aes(x = .estimate, y = outcome, color = .term)) +
  geom_vline(xintercept = 0.5, linetype = 'dashed') +
  geom_boxplot() +
  xlim(0,1) +
  facet_wrap(c('dataset', 'taxlevel')) +
  coord_flip() +
  labs(title = '100x train/test splits - glmnet',
       caption = 'Box: interquartile range. Whisker: min & max') +
  theme_sovacool() +
  theme(legend.position = 'top',
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        plot.caption = element_text(hjust = 0)
  )
```
